Katherine Analysis

### 2018-02-12 Katherine Analysis.Rmd
New clean notebook

---
title: "MSc Statistical Rob correction -Jan29"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    highlight: tango
    theme: cerulean
    toc: yes
  word_document:
    toc: yes
---
# Housekeeping
### Preamble

@@

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
  * `mefa` package version `r packageVersion("mefa")`
  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
  * also requires [rtools](https://cran.r-project.org/bin/windows/Rtools/)

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
library(pvclust)
library(vegan)
library(ggbiplot)
library(factoextra)
```

@@

```{r}
row.has.na <- apply(PlantLength, 1, function(x){any(is.na(x))})
sum(row.has.na) 
PlantLength.filtered <- PlantLength[!row.has.na,]# Removed all the rows with NAs

@@

par(mfrow = c(1,1))
descdist(PlantLength.filtered$Length_plant, discrete = FALSE, boot = 1000)
f1g <- fitdist(PlantLength.filtered$Length_plant, "lnorm") 
f2g <- fitdist(PlantLength.filtered$Length_plant, "norm") 
f3g <- fitdist(PlantLength.filtered$Length_plant, "gamma")
f4g <- fitdist(PlantLength.filtered$Length_plant, "weibull")
f1g$aic
f2g$aic
f3g$aic
f4g$aic

@@

bc<-boxcox(mod1, lambda = seq(-2, 2, 0.1))
lambda <- bc$x[which.max(bc$y)]
PlantLength.filtered <- cbind(PlantLength.filtered, ((PlantLength.filtered$Length_plant^lambda)-1)/lambda)
names(PlantLength.filtered)[5] <- "Yprime"
mod1BC <- lm(Yprime~Location*Species, data=PlantLength.filtered)

@@

### NMDS 
```{r}
# https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/
# https://oliviarata.wordpress.com/2014/04/17/ordinations-in-ggplot2/
#Make a matrix with no row or column equal to 0 (do not enclude the env variable (GM COVERAGE))
M <- as.matrix(FloristicSurvey[1:198,4:55])
M[is.na(M)] <- 0
rownames(M) <- FloristicSurvey$Population
which( colSums(M)==0 )
which( rowSums(M)==0 )
#Now that you know which column must be taken out, redo the matrix but with the last column, then remove the rows and columns =0
#I did this because the previous method doesnt work with the characters in the GM_COVERAGE column.
M <- as.matrix(FloristicSurvey[1:198,4:56])
M[is.na(M)] <- 0
rownames(M) <- FloristicSurvey$Population
M<-M[,-45]
M<-M[-130,]
M<-M[-133,]
M<-M[-132,]
# Now I'll make the env column a vector on its own, but the previous colde now allows it to be in the same order as the matrix im using for distances.
GM_coverage_df <- data.frame(M[,52])
M<-M[,-52]
class(M) <- "numeric"
# with vegdist from Bray to seroeson: add binary = T 
dist_FloristicSurvey <- vegdist(M, method = "bray", binary = T)
#The metaMDS analysis could have done the distance matrix internally but i would rather control it since i have presence/abscence

meta.nmds.FloristicSurvey2D <- metaMDS(dist_FloristicSurvey, k=2, trymax = 1000)

@@

# envfit for the 2D
FloristicSurvey_envfit <- envfit(meta.nmds.FloristicSurvey2D, env = GM_coverage_df, perm = 999) #standard envfit
FloristicSurvey_envfit

@@

## finally plotting.
mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, color=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
    geom_point( aes(color = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
    scale_color_manual(values = c(14,5,19,2))+ 
    coord_cartesian(xlim = c(-1,1.5))+
  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))
```
### PCA
```{r}
FloristicSurvey<-FloristicSurvey[,-56]
FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey))],center = TRUE) 
summary(FloristicSurvey.pca)
fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()

@@

```
*Note that I redid this with GM_coverage_catogory and i didnt find ANY significance!

@@

GLMER_soil <- glmer(Location~scale(Agg_stability)*scale(C_percent)*scale(N_percent)+(1|Population),family=binomial(link='logit'),data=Soil_characteristics)
summary(GLMER_soil)
options(na.action = "na.fail")
dredge(GLMER_soil) 
# A model with nothing is best...
```
# Histology data Analysis

@@

fulldata$pop<-as.factor(fulldata$pop)
# model myc_lesion 
mod1 <- glmmadmb(binlesionF ~ scale(None.Myc)  * scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop), data = fulldata,family = "binomial")
summary(mod1)
mod1.dredge <- dredge(mod1)

# model myc 
mod2 <- glmmadmb(binmycorrF ~ scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop) , data = fulldata,family = "binomial")
summary(mod2)
mod2.dredge <- dredge(mod2)
```

>>>>

---
title: "Katherine Analysis"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    highlight: tango
    theme: cerulean
    toc: yes
---
# Housekeeping
### Preamble

@@

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
  * `mefa` package version `r packageVersion("mefa")`
  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
  * `vegan` package version `r packageVersion("vegan")`
  * `glmmADMB` package version `r packageVersion("glmmADMB")`
  * `car` package version `r packageVersion("car")`
  * `factoextra` package version `r packageVersion("factoextra")`
  * `pvclust` package version `r packageVersion("pvclust")`

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
library(pvclust)
library(vegan)
library(ggbiplot)
library(factoextra)
library(glmmADMB)
library(car)
```

@@

```{r}
row.has.na <- apply(PlantLength, 1, function(x){any(is.na(x))})
sum(row.has.na) 
PlantLength.filtered <- PlantLength[!row.has.na,]# Removed all the rows with NAs
PlantLength.filtered$Pop <- as.factor(PlantLength.filtered$Pop)

@@

@@

bc<-boxcox(mod1, lambda = seq(-2, 2, 0.1))
lambda <- bc$x[which.max(bc$y)]
PlantLength.filtered <- cbind(PlantLength.filtered, ((PlantLength.filtered$Length_plant^lambda)-1)/lambda)
names(PlantLength.filtered)[length(PlantLength.filtered)] <- "Yprime"
mod1BC <- lm(Yprime~Location*Species, data=PlantLength.filtered)

@@

### NMDS 
```{r}
# https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/
# https://oliviarata.wordpress.com/2014/04/17/ordinations-in-ggplot2/
#Make a matrix with no row or column equal to 0 (do not enclude the env variable (GM COVERAGE))
FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("Low", "Med_Low", "Med_High", "High"))
table(FloristicSurvey$GM_Coverage_category)
M <- as.matrix(FloristicSurvey[1:198,4:56])
M[is.na(M)] <- 0
rownames(M) <- FloristicSurvey$Population
M<-M[-c(130,133),]
M<-M[,-45]
GM_coverage_df <- data.frame(M[,52])
M<-M[,-52]
class(M) <- "numeric"

# with vegdist from Bray to seroeson: add binary = T 
dist_FloristicSurvey <- vegdist(M, method = "bray", binary = T)
#The metaMDS analysis could have done the distance matrix internally but i would rather control it since i have presence/abscence
meta.nmds.FloristicSurvey2D <- metaMDS(dist_FloristicSurvey, k=2, trymax = 1000)

@@

FloristicSurvey_envfit <- envfit(meta.nmds.FloristicSurvey2D, env = GM_coverage_df, perm = 999) #standard envfit
FloristicSurvey_envfit

@@

## finally plotting.
mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, color=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
    geom_point( aes(color = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
    scale_color_manual(values = c(14,5,19,2))+ 
    coord_cartesian(xlim = c(-1,1.5))+
  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))
```

### PCA
```{r}
FloristicSurvey<-FloristicSurvey[,-56]
FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey))],center = TRUE) 
summary(FloristicSurvey.pca)
fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()

@@

*Note that I redid this with GM_coverage_catogory and i didnt find ANY significance!

@@

GLMER_soil <- glmer(Location~scale(Agg_stability)*scale(C_percent)*scale(N_percent)+(1|Population),family=binomial(link='logit'),data=Soil_characteristics)
summary(GLMER_soil)
options(na.action = "na.fail")
dredge(GLMER_soil) 
# A model with nothing is best...
```

# Histology data Analysis

@@

fulldata$pop<-as.factor(fulldata$pop)
# model myc_lesion 
mod1 <- glmmadmb(binlesionF ~ scale(None.Myc)  * scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop), data = fulldata,family = "binomial")
summary(mod1)
mod1.dredge <- dredge(mod1)
mod1.dredgegood <- subset(mod1.dredge,mod1.dredge$delta<=7)
# model myc 
mod2 <- glmmadmb(binmycorrF ~ scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop) , data = fulldata,family = "binomial")
summary(mod2)
mod2.dredge <- dredge(mod2)
mod2.dredgegood <- subset(mod2.dredge,mod2.dredge$delta<=7)
```
